##Testing R

load data
```{r}
data <- read.csv("dataset/output.csv")
data
```

Pre-process
```{r}
stance <- data$Stance
sentiment <- data$Sentiment
predicted_sentiment <- data$sentimentVader

stance <- replace(stance, stance=="FAVOR", 1)
stance <- replace(stance, stance=="NONE", 0)
stance <- replace(stance, stance=="AGAINST", -1)
stance <- as.numeric(stance)

sentiment <- replace(sentiment, sentiment=="neg", -1)
sentiment <- replace(sentiment, sentiment=="other", 0)
sentiment <- replace(sentiment, sentiment=="pos", 1)
sentiment <- as.numeric(sentiment)

predicted_sentiment <- replace(predicted_sentiment, predicted_sentiment<0, -1)
predicted_sentiment <- replace(predicted_sentiment, predicted_sentiment>0, 1)
predicted_sentiment <- as.numeric(predicted_sentiment)
```

EXPERIMENTS

Experiment 1) How does sentiment analysis perform compared to the ground-truth?
```{r}
cat(sum(sentiment == predicted_sentiment) / length(sentiment), "% accuracy", sep='')
```

Experiment 2) How does stance detection perform compared to the ground-truth?

Experiment 3) How much overlap is there between ground-truth sentiment and stance?
```{r}
cat(sum(stance == sentiment) / length(stance), "% overlap", sep='')
```

Experiment 4) How much overlap is there between sentiment and stance?

Experiment 5) How do values for sentiment map to values for stance (with bucket sizes of 0.2)?